MP MetaAnalysis

### 2018-12-04 Paper_Analyses.Rmd
first draft General Discussion

[Christina: Big change: I just realized that we also need to report where we could not compute effect sizes, added this info. ]

@@

## Controlling for analysis choices

```{r reanalysis_misp_sens_dv_label}

db_ET_correct$dv_label <- ifelse(db_ET_correct$within_measure=="post", "Post",
                       ifelse(db_ET_correct$within_measure == "pre_post", "Post vs. Pre",
                              "Difference Score"))

db_ET_correct$dv_label <- factor(db_ET_correct$dv_label, levels = c("Post", "Post vs. Pre", "Difference Score"))

rma_correct_DV = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))

#anova(rma_correct_DV, rma_correct)

rma_MP_DV = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))

#anova(rma_MP_DV, rma_MP)

rma_MPeffect_DV <- rma.mv(g_calc, g_var_calc, mods = ~condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))

#anova(rma_MPeffect_DV, rma_MPeffect)

rma_correct_age_DV = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_correct, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))

#anova(rma_correct_age_DV, rma_correct_age)

rma_MP_age_DV = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))

#anova(rma_MP_age_DV, rma_MP_age)

rma_MPeffect_age_DV <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))

#anova(rma_MPeffect_age_DV, rma_MPeffect_age)

```{r reanalysis_misp_sens_post_dur}

rma_correct_post_dur = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))

#anova(rma_correct_post_dur, rma_correct)

rma_MP_post_dur = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))

#anova(rma_MP_post_dur, rma_MP)

rma_MPeffect_post_dur <- rma.mv(g_calc, g_var_calc, mods = ~condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))

#anova(rma_MPeffect_post_dur, rma_MPeffect)

rma_correct_age_post_dur = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_correct, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))

#anova(rma_correct_age_post_dur, rma_correct_age)

rma_MP_age_post_dur = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))

#anova(rma_MP_age_post_dur, rma_MP_age)

rma_MPeffect_age_post_dur <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))

#anova(rma_MPeffect_age_post_dur, rma_MPeffect_age)

@@

What may these results mean for our understanding of phono-lexical development in infancy? Evidence that infants accept a mispronunciation (object identification) while simultaneously holding correctly pronounced and mispronounced labels as separate (mispronunciation sensitivity) may indcate an abstract understanding of words' phonological structure. It appears infants may understand that the mispronunciation and correct pronunciation's phonological form do not match, but that the mispronunciation is a better label for the target compared to the distractor image. The lack of age or vocabulary effects in our meta-analysis suggest that this understanding is present from an age when the earliest words are learned and is maintained throughout early lexical development. Already with the first words, infants have a sense of the importance of sounds in  the words present in their lexicon. We recommend that future theoretical accounts should consider this lack of developmental change.

@@

Then talk about the experimental decisions

** Data Analysis Choices **

  + Post-naming time window size and dependent variable impact misp sensitivity development
  + Offset time does not impact misp sensitivity development
  + the first two do not have theoretical frameworks to guide researchers, whereas offset time does

  [Christina] Did I ask the following already: Do we know whether subtrations were on the trial level? Pre vs post is a bit differnt because it loses the individual bias accommodation and the correlation between pre and post on the participant / item level. 
[Katie] You did. I'll put here my answer from before:
From working with Nivi, we did it participants x condition or participants x trial (but mostly the former). But, this is not something we reported in papers. I don't think I read it at all when putting together the dataset for this either.
[Christina] Mention in the discussion that we don't know this and it might be important to establish standard analysis pipelines for MP studies and that we need open data and code? ;)

When it comes to designing studies, best practices and current standards might not always overlap. Indeed, across a set of previous meta-analyses it was shown that particularly infant research does not adjust sample sizes according to the effect in question (Bergmann et al., in press). A meta-analysis is a first step in improving experiment planning by measuring the underlying effect and its variance, which is directly related to the sample needed to achieve satisfactory power in the null hypothesis significance testing framework. Failing to take effect sizes into account can both yield to underpowered research and to testing too many participants, both consequences are undesirable for a number of reasons that have been discussed in depth elsewhere. We will just briefly mention two that we consider most salient for theory building: Underpowered studies will lead to false negatives more frequently than expected, which in turn results in an unpublished body of literature (citationcitation). Overpowered studies mean that participants were tested unnecessarily, which has substantial ethical consequences particularly when working with infants and other difficult to recruit and test populations.

From Christina: let's make a note to put sth in the discussion about our curve being surprisingly flat for correctly pronounced words bc people adapt their analysis windows? Bc if you look at Molly's reaction time paper, there is a steep increase.

>>>>

@@

@@

Evidence that infants accept a mispronunciation (object identification) while simultaneously holding correctly pronounced and mispronounced labels as separate (mispronunciation sensitivity) may indcate an abstract understanding of words' phonological structure. It appears that young infants may understand that the mispronunciation and correct pronunciation's phonological form do not match (phonological distinctiveness), but that the mispronunciation is a better label for the target compared to the distractor image (phonological constancy).  The lack of age or vocabulary effects in our meta-analysis suggest that this understanding is present from an age when the earliest words are learned and is maintained throughout early lexical development. This implies mastery of the principles of phonological constancy and phonological distinctiveness at an age earlier than previously thought, which we recommend should be taken into account by future theoretical accounts.

@@

While creating the dataset on which this meta-analysis was based, we included as many details as possible to describe each study. During the coding of these characteristics, we noted a potential for variation in a handful of variables that relate to data analysis, specifically relating to timing (size of time window analyzed; offset time) and which dependent variable(s) were reported. We focused on these variables in particular because their choice can potentially be made after researchers have examined the data, leading to an inflated increase of significant results which may also explain the publication bias observed in the funnel plot assymmetry (Simmons, Nelson, & Simonsohn, 2011). To explore whether this variation contributed to the lack of developmental change observed in the overall meta-analysis, we included these variables as moderators in a set of exploratory analyses. We noted an interesting pattern of results, specifically that different conclusions about mispronunciation sensitivity, but more notably mispronunciation sensitivity development, could be drawn depending on the length of the post-naming time window analyzed as well as the type of dependent variable calculated in the experiment.

Considering the timing variable, infants are expected to recognize words more quickly with age (Fernald, Swingley & Pinto, 2001; Swingley, Pinto & Fernald, 1999; Swingley & Fernald, 2002). This evidence has often guided decisions for the post-naming time window to be analyzed in mispronunciation sensitivity studies, including where to begin the time window (offset time) and how long this window should be (post-naming time window analyzed). Specifically, increasing age should lead to quicker reaction times, and therefore lower offset times. Yet, we found no evidence for a relationship between offset time and infant age nor that offset time modulated mispronunciation sensitivity. Indeed, a large majority used an offset time between 360 and 370 ms, which follows the best guess of Swingley and Aslin (2000) for the amount of time needed for infants to initiate eye movements in response to a spoken target word.

In contrast, the length of the post-naming window analyzed was related to infant age and also found to modulate mispronunciation sensitivity. Younger infants may take longer to reliably identify the target image, and as a result the length of the post-naming time window analyzed may be longer in younger infants. This was born out in the meta-analysis: studies that tested younger infants used a longer post-naming time window. Longer post-naming time windows, however, resulted in a smaller effect size for mispronunciation sensitivity. Critically, the developmental trajectory of mispronunciation sensitivity changed depending on the length of the post-naming time window analyzed. Longer time windows resulted in decreasing or no change in mispronunciation sensitivity, while shorter time windows resulting in increasing mispronunciation sensitivity. Given a set of mispronunciation sensitivity data, a conclusion regarding the development of mispronunciation sensitivity would be different depending on the length of the post-naming time window analyzed.

Unlike the timing variables, the origin of a potential relationship between the type of dependent variable calculated and mispronunciation sensitivity is much less clear. The majority of studies created a Difference Score, subtracting pre-naming phase PTL from that of post-naming phase PTL, while the remaining studies compared pre-naming PTL with post-naming PTL (Pre vs. Post) or analyzed post-naming PTL alone (Post). Both the Difference Score and the Pre vs. Post dependent variables consider pre-naming phase preferences for the target compared to distractor image, but were found to differentially modulate mispronunciation sensitivity. There was no difference in mispronunciation sensitivity between the Post and Difference Score dependent variables, but in comparison to Post, studies that reported the Pre vs. Post dependent variable had lower effect sizes for mispronunciation sensitivity. Furthermore, studies reporting the Pre vs. Post dependent variable showed decreasing mispronunciation sensitivity with age, while studies reporting a Difference Score or Post dependent variable showed an increase. Similar to the length of the post-naming time window analyzed, given a set of mispronunciation sensitivity data, a conclusion regarding the development of mispronunciation sensitivity would be different depending on the choice of dependent variable.

Without access to the full datasets of the studies included in this meta-analysis, it is difficult to pinpoint the exact role played by these data analysis choices, specificially the length of the post-naming time window analyzed and the type of dependent variable reported. Access to such data would allow for a systematic analysis of the influence of these choices on the size of the effect of mispronunciation sensitivity as well as its developmental trajectory. Furthermore, sharing analysis code would allow for a clearer understanding of the approach to data analysis. For example, the Difference Score dependent variable substracts the pre-naming phase PTL from the post-naming phase PTL. Some studies compute this variable on the level of condition (e.g. White & Morgan, 2008), but this reduces SOMETHING, WHICH IS A BAD SOMETHING [Katie]. In addition to shared data and code, it may be useful to establish standard analysis pipelines for mispronunciation studies. This would allow for a more uniform analysis of this phenomenon, as well as aid experimenters in future research planning. Finally, we recommend that experimenters consider analyzing the time course as a whole, instead of aggregating the proportion of target looking behavior over the entire trial. Both Growth Curve Analysis (Mirman et al., 2008; Law & Edwards, 2015) and Permutation Clusters Analysis (Maris & Oostenveld, 2007; Von Holzen & Mani, 2012) offer potential solutions for time course analysis.

### 2018-12-04 Paper_Analyses.tex
first draft General Discussion

{[}Christina: Big change: I just realized that we also need to report
where we could not compute effect sizes, added this info. {]}

@@

\begin{longtable}{lllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:SummaryTable}Summary of all studies.}\\
\toprule
Paper & Publication format & Age & Vocabulary & N Effect Sizes\\
\midrule
Altvater-Mackensen (2010) & dissertation & 22, 25 & None & 13\\
Altvater-Mackensen et al. (2014) & paper & 18, 25 & None & 16\\
Bailey \& Plunkett (2002) & paper & 18, 24 & Comp & 12\\
Bergelson \& Swingley (2017) & paper & 6, 7, 9, 12 & None & 9\\
Bernier \& White (2017) & proceedings & 21 & None & 4\\
Delle Luche et al. (2015) & paper & 20, 19 & None & 4\\
Durrant et al. (2014) & paper & 19, 20 & None & 4\\
Höhle et al. (2006) & paper & 18 & None & 4\\
Højen et al. (n.d.) & gray paper & 19, 20 & Comp/Prod & 6\\
Mani \& Plunkett (2007) & paper & 15, 18, 24, 14, 20 & Comp/Prod & 14\\
Mani \& Plunkett (2010) & paper & 12 & Comp & 8\\
Mani \& Plunkett (2011) & paper & 23, 17 & None & 15\\
Mani, Coleman, \& Plunkett (2008) & paper & 18 & Comp/Prod & 4\\
Ramon-Casas \& Bosch (2010) & paper & 24, 25 & None & 4\\
Ramon-Casas et al. (2009) & paper & 21, 20, 43, 44 & Prod & 14\\
Ren \& Morgan (in press) & gray paper & 19 & None & 8\\
Skoruppa et al. (2013) & paper & 23 & None & 4\\
Swingley (2003) & paper & 19 & Comp/Prod & 6\\
Swingley (2009) & paper & 17 & Comp/Prod & 4\\
Swingley (2016) & paper & 27, 28 & Prod & 9\\
Swingley \& Aslin (2000) & paper & 20 & Comp & 2\\
Swingley \& Aslin (2002) & paper & 15 & Comp/Prod & 4\\
Tamasi (2016) & dissertation & 30 & None & 4\\
Tao \& Qinmei (2013) & paper & 12 & None & 4\\
Tao et al. (2012) & paper & 16 & Comp & 6\\
van der Feest \& Fikkert, (2015) & paper & 24, 20 & None & 16\\
van der Feest \& Johnson (2016) & paper & 24 & None & 24\\
Wewalaarachchi et al. (2017) & paper & 24 & None & 8\\
White \& Aslin (2011) & paper & 18 & None & 4\\
White \& Morgan (2008) & paper & 18, 19 & None & 12\\
Zesiger \& Jöhr (2011) & paper & 14 & None & 8\\
Zesiger et al. (2012) & paper & 12, 19 & Comp/Prod & 6\\
\bottomrule
\end{longtable}
\end{lltable}

We first generated a list of potentially relevant items to be included
in our meta-analysis by creating an expert list. This process yielded
110 items. We then used the google scholar search engine to search for
papers citing the original Swingley \& Aslin (2000) publication. This
search was conducted on 22 September, 2017 and yielded 288 results. We
removed 99 duplicate items and screened the remaining 299 items for
their title and abstract to determine whether each met the following
inclusion criteria: (1) original data was reported; (2) the experiment
examined familiar word recognition and mispronunciations; (3) infants
studied were under 31-months-of-age and typically developing; (4) the
dependent variable was derived from proportion of looks to a target
image versus a distractor in a eye movement experiment; (5) the stimuli
were auditory speech. The final sample (n = \emph{32}) consisted of 27
journal articles, 1 proceedings paper, 2 thesis, and 2 unpublished
reports. We will refer to these items collectively as papers. Table 1
provides an overview of all papers included in the present
meta-analysis.

@@

The 32 papers we identified as relevant were then coded with as much
consistently reported detail as possible (Tsuji, Bergmann, \& Cristia,
2014; Bergmann et al., 2018). For each experiment (note that a paper
typically has multiple experiments), we entered variables describing the
publication, population, experiment design and stimuli, and results. For
the planned analyses to evaluate the development of mispronunciation
sensitivity, we focus on the following characteristics:

@@

We separated conditions according to whether or not the target word was
mispronounced to be able to investigate infants' looking to the target
picture as well as their mispronunciation sensitivity, which is the
difference between looks to the target in correct and mispronounced
trials. When the same infants were further exposed to multiple
mispronunciation conditions and the results were reported separately in
the paper, we also entered each condition as a separate row (e.g.,
consonant versus vowel mispronunciations; Mani \& Plunkett, 2007). The
fact that the same infants contributed data to multiple rows (minimally
those containing information on correct and mispronounced trials) leads
to shared variance across effect sizes, which we account for in our
analyses (see next section). We will call each row a record; in total
there were 260 records in our data.

@@

We calculated Hedges' \emph{g} using the raw means and standard
deviations reported in the paper (\emph{n} = 186 records from 26 papers)
or using reported t-values (\emph{n} = 74 records from 9 papers). Two
papers reported raw means and standard deviations for some experimental
conditions and just t-values for the remaining experimental conditions
(Swingley, 2016; Altvater-Mackensen et al., 2014). Raw means and
standard deviations were extracted from figures for 3 papers. In a
within-participation design, when two means are compared (i.e.~looking
during pre- and post-naming) it is necessary to obtain correlations
between the two measurements at the participant level to calculate
effect sizes and effect size variance based on t-values. Upon request we
were provided with correlation values for one paper (Altvater-Mackensen,
2010); we were able to compute correlations using means, standard
deviations, and t-values for \emph{n} = 5 (following Csibra, et al.
2016, Appendix B; see also Rabagliati, Ferguson, \& Lew-Williams, 2018).
Correlations were imputed for the remaining papers (see Black \&
Bergmann, 2017, for the same procedure). For two papers, we could not
derive any effect size (Ballem \& Plunkett, Renner), and for a third
paper, we do not have sufficient information in one record to compute
effect sizes (Skoruppa). We compute a total of 106 effect sizes for
correct pronunciations and 150 for mispronunciations. Following standard
meta-analytic practice, we remove outliers, i.e.~effect sizes more than
3 standard deviations from the respective mean effect size. This leads
to the exclusion of 2 records for correct pronunciations and 3 records
for mispronunciations.

@@

\subsection{Controlling for analysis
choices}\label{controlling-for-analysis-choices}

@@

Then talk about the experimental decisions

** Data Analysis Choices **

\begin{itemize}
\tightlist
\item
  Post-naming time window size and dependent variable impact misp
  sensitivity development
\item
  Offset time does not impact misp sensitivity development
\item
  the first two do not have theoretical frameworks to guide researchers,
  whereas offset time does
\end{itemize}

{[}Christina{]} Did I ask the following already: Do we know whether
subtrations were on the trial level? Pre vs post is a bit differnt
because it loses the individual bias accommodation and the correlation
between pre and post on the participant / item level. {[}Katie{]} You
did. I'll put here my answer from before: From working with Nivi, we did
it participants x condition or participants x trial (but mostly the
former). But, this is not something we reported in papers. I don't think
I read it at all when putting together the dataset for this either.
{[}Christina{]} Mention in the discussion that we don't know this and it
might be important to establish standard analysis pipelines for MP
studies and that we need open data and code? ;)

When it comes to designing studies, best practices and current standards
might not always overlap. Indeed, across a set of previous meta-analyses
it was shown that particularly infant research does not adjust sample
sizes according to the effect in question (Bergmann et al., in press). A
meta-analysis is a first step in improving experiment planning by
measuring the underlying effect and its variance, which is directly
related to the sample needed to achieve satisfactory power in the null
hypothesis significance testing framework. Failing to take effect sizes
into account can both yield to underpowered research and to testing too
many participants, both consequences are undesirable for a number of
reasons that have been discussed in depth elsewhere. We will just
briefly mention two that we consider most salient for theory building:
Underpowered studies will lead to false negatives more frequently than
expected, which in turn results in an unpublished body of literature
(citationcitation). Overpowered studies mean that participants were
tested unnecessarily, which has substantial ethical consequences
particularly when working with infants and other difficult to recruit
and test populations.

From Christina: let's make a note to put sth in the discussion about our
curve being surprisingly flat for correctly pronounced words bc people
adapt their analysis windows? Bc if you look at Molly's reaction time
paper, there is a steep increase.

>>>>

@@

\begin{longtable}{lllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:SummaryTable}Summary of all studies.}\\
\toprule
Paper & Publication format & Age & Vocabulary & N Effect Sizes\\
\midrule
Altvater-Mackensen (2010) & dissertation & 22, 25 & None & 13\\
Altvater-Mackensen et al. (2014) & paper & 18, 25 & None & 16\\
Bailey \& Plunkett (2002) & paper & 18, 24 & Comp & 12\\
Ballem \& Plunkett (2005) & paper & 14 & None & 4\\
Bergelson \& Swingley (2017) & paper & 6, 7, 9, 12 & None & 9\\
Bernier \& White (2017) & proceedings & 21 & None & 4\\
Delle Luche et al. (2015) & paper & 20, 19 & None & 4\\
Durrant et al. (2014) & paper & 19, 20 & None & 4\\
Höhle et al. (2006) & paper & 18 & None & 4\\
Højen et al. (n.d.) & gray paper & 19, 20 & Comp/Prod & 6\\
Mani \& Plunkett (2007) & paper & 15, 18, 24, 14, 20 & Comp/Prod & 14\\
Mani \& Plunkett (2010) & paper & 12 & Comp & 8\\
Mani \& Plunkett (2011) & paper & 23, 17 & None & 15\\
Mani, Coleman, \& Plunkett (2008) & paper & 18 & Comp/Prod & 4\\
Ramon-Casas \& Bosch (2010) & paper & 24, 25 & None & 4\\
Ramon-Casas et al. (2009) & paper & 21, 20, 43, 44 & Prod & 14\\
Ren \& Morgan (in press) & gray paper & 19 & None & 8\\
Renner (2017) & dissertation & 17, 24 & None & 6\\
Skoruppa et al. (2013) & paper & 23 & None & 5\\
Swingley (2003) & paper & 19 & Comp/Prod & 6\\
Swingley (2009) & paper & 17 & Comp/Prod & 4\\
Swingley (2016) & paper & 27, 28 & Prod & 9\\
Swingley \& Aslin (2000) & paper & 20 & Comp & 2\\
Swingley \& Aslin (2002) & paper & 15 & Comp/Prod & 4\\
Tamasi (2016) & dissertation & 30 & None & 4\\
Tao \& Qinmei (2013) & paper & 12 & None & 4\\
Tao et al. (2012) & paper & 16 & Comp & 6\\
van der Feest \& Fikkert, (2015) & paper & 24, 20 & None & 16\\
van der Feest \& Johnson (2016) & paper & 24 & None & 24\\
Wewalaarachchi et al. (2017) & paper & 24 & None & 8\\
White \& Aslin (2011) & paper & 18 & None & 4\\
White \& Morgan (2008) & paper & 18, 19 & None & 12\\
Zesiger \& Jöhr (2011) & paper & 14 & None & 8\\
Zesiger et al. (2012) & paper & 12, 19 & Comp/Prod & 6\\
\bottomrule
\end{longtable}
\end{lltable}

We first generated a list of potentially relevant items to be included
in our meta-analysis by creating an expert list. This process yielded
110 items. We then used the google scholar search engine to search for
papers citing the original Swingley \& Aslin (2000) publication. This
search was conducted on 22 September, 2017 and yielded 288 results. We
removed 99 duplicate items and screened the remaining 299 items for
their title and abstract to determine whether each met the following
inclusion criteria: (1) original data was reported; (2) the experiment
examined familiar word recognition and mispronunciations; (3) infants
studied were under 31-months-of-age and typically developing; (4) the
dependent variable was derived from proportion of looks to a target
image versus a distractor in a eye movement experiment; (5) the stimuli
were auditory speech. The final sample (n = \emph{34}) consisted of 28
journal articles, 1 proceedings paper, 3 thesis, and 2 unpublished
reports. We will refer to these items collectively as papers. Table 1
provides an overview of all papers included in the present
meta-analysis.

@@

The 34 papers we identified as relevant were then coded with as much
consistently reported detail as possible (Tsuji, Bergmann, \& Cristia,
2014; Bergmann et al., 2018). For each experiment (note that a paper
typically has multiple experiments), we entered variables describing the
publication, population, experiment design and stimuli, and results. For
the planned analyses to evaluate the development of mispronunciation
sensitivity, we focus on the following characteristics:

@@

We separated conditions according to whether or not the target word was
mispronounced to be able to investigate infants' looking to the target
picture as well as their mispronunciation sensitivity, which is the
difference between looks to the target in correct and mispronounced
trials. When the same infants were further exposed to multiple
mispronunciation conditions and the results were reported separately in
the paper, we also entered each condition as a separate row (e.g.,
consonant versus vowel mispronunciations; Mani \& Plunkett, 2007). The
fact that the same infants contributed data to multiple rows (minimally
those containing information on correct and mispronounced trials) leads
to shared variance across effect sizes, which we account for in our
analyses (see next section). We will call each row a record; in total
there were 271 records in our data.

@@

We calculated Hedges' \emph{g} using the raw means and standard
deviations reported in the paper (\emph{n} = 186 records from 26 papers)
or using reported t-values (\emph{n} = 74 records from 9 papers). Two
papers reported raw means and standard deviations for some experimental
conditions and just t-values for the remaining experimental conditions
(Swingley, 2016; Altvater-Mackensen et al., 2014). Raw means and
standard deviations were extracted from figures for 4 papers. In a
within-participation design, when two means are compared (i.e.~looking
during pre- and post-naming) it is necessary to obtain correlations
between the two measurements at the participant level to calculate
effect sizes and effect size variance based on t-values. Upon request we
were provided with correlation values for one paper (Altvater-Mackensen,
2010); we were able to compute correlations using means, standard
deviations, and t-values for \emph{n} = 5 (following Csibra, et al.
2016, Appendix B; see also Rabagliati, Ferguson, \& Lew-Williams, 2018).
Correlations were imputed for the remaining papers (see Black \&
Bergmann, 2017, for the same procedure). For two papers, we could not
derive any effect size (Ballem \& Plunkett, Renner), and for a third
paper, we do not have sufficient information in one record to compute
effect sizes (Skoruppa). We compute a total of 106 effect sizes for
correct pronunciations and 150 for mispronunciations. Following standard
meta-analytic practice, we remove outliers, i.e.~effect sizes more than
3 standard deviations from the respective mean effect size. This leads
to the exclusion of 2 records for correct pronunciations and 3 records
for mispronunciations.

@@

@@

While creating the dataset on which this meta-analysis was based, we
included as many details as possible to describe each study. During the
coding of these characteristics, we noted a potential for variation in a
handful of variables that relate to data analysis, specifically relating
to timing (size of time window analyzed; offset time) and which
dependent variable(s) were reported. We focused on these variables in
particular because their choice can potentially be made after
researchers have examined the data, leading to an inflated increase of
significant results which may also explain the publication bias observed
in the funnel plot assymmetry (Simmons, Nelson, \& Simonsohn, 2011). To
explore whether this variation contributed to the lack of developmental
change observed in the overall meta-analysis, we included these
variables as moderators in a set of exploratory analyses. We noted an
interesting pattern of results, specifically that different conclusions
about mispronunciation sensitivity, but more notably mispronunciation
sensitivity development, could be drawn depending on the length of the
post-naming time window analyzed as well as the type of dependent
variable calculated in the experiment.

Considering the timing variable, infants are expected to recognize words
more quickly with age (Fernald, Swingley \& Pinto, 2001; Swingley, Pinto
\& Fernald, 1999; Swingley \& Fernald, 2002). This evidence has often
guided decisions for the post-naming time window to be analyzed in
mispronunciation sensitivity studies, including where to begin the time
window (offset time) and how long this window should be (post-naming
time window analyzed). Specifically, increasing age should lead to
quicker reaction times, and therefore lower offset times. Yet, we found
no evidence for a relationship between offset time and infant age nor
that offset time modulated mispronunciation sensitivity. Indeed, a large
majority used an offset time between 360 and 370 ms, which follows the
best guess of Swingley and Aslin (2000) for the amount of time needed
for infants to initiate eye movements in response to a spoken target
word.

In contrast, the length of the post-naming window analyzed was related
to infant age and also found to modulate mispronunciation sensitivity.
Younger infants may take longer to reliably identify the target image,
and as a result the length of the post-naming time window analyzed may
be longer in younger infants. This was born out in the meta-analysis:
studies that tested younger infants used a longer post-naming time
window. Longer post-naming time windows, however, resulted in a smaller
effect size for mispronunciation sensitivity. Critically, the
developmental trajectory of mispronunciation sensitivity changed
depending on the length of the post-naming time window analyzed. Longer
time windows resulted in decreasing or no change in mispronunciation
sensitivity, while shorter time windows resulting in increasing
mispronunciation sensitivity. Given a set of mispronunciation
sensitivity data, a conclusion regarding the development of
mispronunciation sensitivity would be different depending on the length
of the post-naming time window analyzed.

Unlike the timing variables, the origin of a potential relationship
between the type of dependent variable calculated and mispronunciation
sensitivity is much less clear. The majority of studies created a
Difference Score, subtracting pre-naming phase PTL from that of
post-naming phase PTL, while the remaining studies compared pre-naming
PTL with post-naming PTL (Pre vs.~Post) or analyzed post-naming PTL
alone (Post). Both the Difference Score and the Pre vs.~Post dependent
variables consider pre-naming phase preferences for the target compared
to distractor image, but were found to differentially modulate
mispronunciation sensitivity. There was no difference in
mispronunciation sensitivity between the Post and Difference Score
dependent variables, but in comparison to Post, studies that reported
the Pre vs.~Post dependent variable had lower effect sizes for
mispronunciation sensitivity. Furthermore, studies reporting the Pre
vs.~Post dependent variable showed decreasing mispronunciation
sensitivity with age, while studies reporting a Difference Score or Post
dependent variable showed an increase. Similar to the length of the
post-naming time window analyzed, given a set of mispronunciation
sensitivity data, a conclusion regarding the development of
mispronunciation sensitivity would be different depending on the choice
of dependent variable.

Without access to the full datasets of the studies included in this
meta-analysis, it is difficult to pinpoint the exact role played by
these data analysis choices, specificially the length of the post-naming
time window analyzed and the type of dependent variable reported. Access
to such data would allow for a systematic analysis of the influence of
these choices on the size of the effect of mispronunciation sensitivity
as well as its developmental trajectory. Furthermore, sharing analysis
code would allow for a clearer understanding of the approach to data
analysis. For example, the Difference Score dependent variable
substracts the pre-naming phase PTL from the post-naming phase PTL. Some
studies compute this variable on the level of condition (e.g.~White \&
Morgan, 2008), but this reduces SOMETHING, WHICH IS A BAD SOMETHING
{[}Katie{]}. In addition to shared data and code, it may be useful to
establish standard analysis pipelines for mispronunciation studies. This
would allow for a more uniform analysis of this phenomenon, as well as
aid experimenters in future research planning. Finally, we recommend
that experimenters consider analyzing the time course as a whole,
instead of aggregating the proportion of target looking behavior over
the entire trial. Both Growth Curve Analysis (Mirman et al., 2008; Law
\& Edwards, 2015) and Permutation Clusters Analysis (Maris \&
Oostenveld, 2007; Von Holzen \& Mani, 2012) offer potential solutions
for time course analysis.

### 2018-12-04 Paper_Analyses_sandbox.Rmd
updated methods/results
first draft General Discussion

# mf <- subset(dat_f, n_feature == "3")
# min_age <- min(mf$mean_age_1)
# max_age <- max(mf$mean_age_1)
# 
# dat_fage= dat_f%>%
#   filter(mean_age_1>=min_age&mean_age_1<=max_age)

@@

>>>>

@@

## Controlling for analysis choices

```{r reanalysis_misp_sens_dv_label}

dat$dv_label <- ifelse(dat$within_measure=="post", "Post",
                       ifelse(dat$within_measure == "pre_post", "Post vs. Pre",
                              "Difference Score"))

dat$dv_label <- factor(dat$dv_label, levels = c("Post", "Post vs. Pre", "Difference Score"))

db_ET_MP$dv_label <- ifelse(db_ET_MP$within_measure=="post", "Post",
                       ifelse(db_ET_MP$within_measure == "pre_post", "Post vs. Pre",
                              "Difference Score"))

db_ET_MP$dv_label <- factor(db_ET_MP$dv_label, levels = c("Post", "Post vs. Pre", "Difference Score"))

db_ET_correct$dv_label <- ifelse(db_ET_correct$within_measure=="post", "Post",
                       ifelse(db_ET_correct$within_measure == "pre_post", "Post vs. Pre",
                              "Difference Score"))

db_ET_correct$dv_label <- factor(db_ET_correct$dv_label, levels = c("Post", "Post vs. Pre", "Difference Score"))

rma_correct_DV = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))

#anova(rma_correct_DV, rma_correct)

rma_MP_DV = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))

#anova(rma_MP_DV, rma_MP)

rma_MPeffect_DV <- rma.mv(g_calc, g_var_calc, mods = ~condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))

#anova(rma_MPeffect_DV, rma_MPeffect)

rma_correct_age_DV = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_correct, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))

#anova(rma_correct_age_DV, rma_correct_age)

rma_MP_age_DV = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))

#anova(rma_MP_age_DV, rma_MP_age)

rma_MPeffect_age_DV <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ dv_label | short_cite))

#anova(rma_MPeffect_age_DV, rma_MPeffect_age)

```{r reanalysis_misp_sens_post_dur}

rma_correct_post_dur = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))

#anova(rma_correct_post_dur, rma_correct)

rma_MP_post_dur = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))

#anova(rma_MP_post_dur, rma_MP)

rma_MPeffect_post_dur <- rma.mv(g_calc, g_var_calc, mods = ~condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))

#anova(rma_MPeffect_post_dur, rma_MPeffect)

rma_correct_age_post_dur = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_correct, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))

#anova(rma_correct_age_post_dur, rma_correct_age)

rma_MP_age_post_dur = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_MP, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))

#anova(rma_MP_age_post_dur, rma_MP_age)

rma_MPeffect_age_post_dur <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition, data = dat, random = list(~ same_infant_calc | short_cite, ~ as.factor(post_nam_dur) | short_cite))

#anova(rma_MPeffect_age_post_dur, rma_MPeffect_age)
